Blocks of extended ancestry around selected loci in hybrid zones

### 2016-03-01 drafts/hybrid_zone.tex
one minor typo

There is great interest in identifying the loci that are experiencing selection in hybrid zones. Popular approaches to this involve identifying alleles that are exceptional in terms of frequency across space, or genome-wide admixture proportion \citep{Porter1997,Gompert2012}.  
Current genomic resources, however, can provide an additional rich information when applied to the study of hybrid zones.
In particular, ancestry deconvolution facilitated by programs such as  hapMIX \citep{Price2009}, LAMP \citep{Sankararaman2008} and fineSTRUCTURE \citep{Lawson2012} provides researchers with a measure of the length of ancestry tracts across the genome and this information has been used extensively to infer the demographic history of hybridization/admixture from present day samples \citep[e.g. ][]{Hellenthal2014}. 
In order to interpret these patterns in the context of a hybrid zone, we set out to understand the impact of selection on patterns of ancestry tract lengths, and here present an expectation of block-length patterns throughout a hybrid zone. 
Importantly, we find that selection against hybrid incompatibilities leaves a distinct genomic signature in the form of long contiguous blocks of ancestry around these loci.
This pattern reflects the intuition that regions surrounding selected loci introgress less readily, and loci under selection can therefore be thought as moving under Brownian motion with drift whereby a lineage that is presently on the `` wrong" side of a hybrid zone rapidly moves, backwards in time, across space to the ``correct" side. 
In other words, disadvantageous alleles that have encroached deep into the other side of the hybrid zone have done so by chance and, since they do not persist for long on the ``wrong" side, are likely to have done so relatively recently. Haplotypes surrounding the selected locus therefore have had relatively few opportunities for recombination with different ancestries and this is reflected in longer blocks of contiguous ancestry.

>>>>

There is great interest in identifying the loci that are experiencing selection in hybrid zones. Popular approaches to this involve identifying alleles that are exceptional in terms of frequency across space, or genome-wide admixture proportion \citep{Porter1997,Gompert2012}.  
Current genomic resources, however, can provide an additional rich information when applied to the study of hybrid zones.
In particular, ancestry deconvolution facilitated by programs such as  hapMIX \citep{Price2009}, LAMP \citep{Sankararaman2008} and fineSTRUCTURE \citep{Lawson2012} provides researchers with a measure of the length of ancestry tracts across the genome and this information has been used extensively to infer the demographic history of hybridization/admixture from present day samples \citep[e.g. ][]{Hellenthal2014}. 
In order to interpret these patterns in the context of a hybrid zone, we set out to understand the impact of selection on patterns of ancestry tract lengths, and here present an expectation of block-length patterns throughout a hybrid zone. 
Importantly, we find that selection against hybrid incompatibilities leaves a distinct genomic signature in the form of long contiguous blocks of ancestry around these loci.
This pattern reflects the intuition that regions surrounding selected loci introgress less readily, and loci under selection can therefore be thought as moving under Brownian motion with drift whereby a lineage that is presently on the ``wrong" side of a hybrid zone rapidly moves, backwards in time, across space to the ``correct" side. 
In other words, disadvantageous alleles that have encroached deep into the other side of the hybrid zone have done so by chance and, since they do not persist for long on the ``wrong" side, are likely to have done so relatively recently. Haplotypes surrounding the selected locus therefore have had relatively few opportunities for recombination with different ancestries and this is reflected in longer blocks of contiguous ancestry.
